We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-02 paper/paper.tex
+1 paragraph

\begin{abstract}
In this paper we quantify the joint spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify the
expected deviations from statistically spherical satellite
distributions in the Lambda Cold Dark Matter paradigm. 
We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of deviation from
sphericity.
This makes the LG a $3\sigma$ outlier, with all the weight lying on
the extremly planar MW satellite distribution.
\end{abstract}

@@

The comparison between the normalized quantities is the one that
carries the important information about the deviations from spheriticy.

>>>>

\begin{abstract}
In this paper we quantify the deviations from sphericity in the spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify the
same deviations from sphericity in the Lambda Cold Dark Matter paradigm. 
We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of deviation from
sphericity.
This makes the LG a $3\sigma$ outlier, with all the weight lying on
the extremly planar MW satellite distribution.
\end{abstract}

@@

The comparison between the normalized quantities is the one that
carries the important information about the deviations from
spheriticy. 
We do not want to directly compare how the results observations
deviate from simulations but to compare the deviations from
asphericity in observations and simulations.

It
